---
title: "Static SQL"
author: "Enrique ESCOBAR"
date: "18-11-2016"
output: 
  html_document: 
    toc: yes
---

# Setup R
The best tool to do statistical analysis and graph is R (integrated in SQL Server 2016).

# Set path and load libraries
```{r SetupPathLibs, echo=TRUE, error=FALSE, message=TRUE, warning=FALSE}
# namespace
aNamespace <- "SqlServerProfiler";
#setwd("C:\\Users\\Admin\\Desktop"); #USERPROFILE
#setwd("D:/Disk_X/axon/SqlServerProfiler");
setwd("E:/Disk_X/SqlServerProfiler/");
# base lib
gDriveUtil <- paste0(c("Lib/", aNamespace, ".Util.R"), sep = "", collapse = "");
write(paste0(c("Load Util........\t", gDriveUtil), sep = "", collapse = ""), stdout());
source(gDriveUtil);
# fileList0 <- list("Data/00 Scripts start.new.xls");
# fileList1 <- list("Data/01 Agent Niveau 1 - Evelyne made mistake and logged out.new.xls");
# fileList2 <- list("Data/02 Agent N1 Complete Agent Web Services engage.new.xls");
# fileList3 <- list("Data/03 Agent N1 complete.new.1of5.xls",
#                   "Data/03 Agent N1 complete.new.2of5.xls",
#                   "Data/03 Agent N1 complete.new.3of5.xls",
#                   "Data/03 Agent N1 complete.new.4of5.xls",
#                   "Data/03 Agent N1 complete.new.5of5.xls");
# fileList4 <- list("Data/04 Agent N2 complete.new.1of3.xls",
#                   "Data/04 Agent N2 complete.new.2of3.xls",
#                   "Data/04 Agent N2 complete.new.3of3.xls");
# fileList5 <- list("Data/05 Sup SAC.new.xls");
# #
# xlsxTibble0 <- ScreenXmlXlsFiles(fileList0);
# TraceXmlXlsToCsv(xlsxTibble0, filePath = "Data/00 Scripts start.new.csv");
# rm(xlsxTibble0);
# xlsxTibble1 <- ScreenXmlXlsFiles(fileList1);
# TraceXmlXlsToCsv(xlsxTibble1, filePath = "Data/01 Agent Niveau 1 - Evelyne made mistake and logged out.new.csv");
# rm(xlsxTibble1);
# xlsxTibble2 <- ScreenXmlXlsFiles(fileList2);
# TraceXmlXlsToCsv(xlsxTibble2, filePath = "Data/02 Agent N1 Complete Agent Web Services engage.new.csv");
# rm(xlsxTibble2);
# xlsxTibble3 <- ScreenXmlXlsFiles(fileList3);
# TraceXmlXlsToCsv(xlsxTibble3, filePath = "Data/03 Agent N1 complete.new.csv");
# rm(xlsxTibble3);
# xlsxTibble4 <- ScreenXmlXlsFiles(fileList4);
# TraceXmlXlsToCsv(xlsxTibble4, filePath = "Data/04 Agent N2 complete.new.csv");
# rm(xlsxTibble4);
# xlsxTibble5 <- ScreenXmlXlsFiles(fileList5);
# TraceXmlXlsToCsv(xlsxTibble5, filePath = "Data/05 Sup SAC.new.csv");
# rm(xlsxTibble5);
# txtFiles <- list("Data/00 Scripts start.new.txt",
#             "Data/01 Agent Niveau 1 - Evelyne made mistake and logged out.new.txt",
#             "Data/02 Agent N1 Complete Agent Web Services engage.new.txt",
#             "Data/03 Agent N1 complete.new.txt",
#             "Data/04 Agent N2 complete.new.txt",
#             "Data/05 Sup SAC.new.txt");
# ScreenTxtFiles(fileList = txtFiles);
```

# Connexion & server info
```{r ServerInfo, echo=TRUE, error=FALSE, message=TRUE, warning=FALSE}
print("Server");
# Server info
serverInstance <- XlsToDataFrameSingleRow(xlsFile = "Data/HYSEC-SQLServerInstance.xls")$SQLServerInstance;
serverInstance <- as.character(serverInstance);
serverVersion <- XlsToDataFrameSingleRow(xlsFile = "Data/HYSEC-SQLServerVersion.xls")$SQLServerVersion;
serverVersion <- as.character(serverVersion);
serverService <- XlsToDataFrameSingleRow(xlsFile = "Data/HYSEC-ServiceInstance.xls")$ServiceInstance;
serverService <- as.character(serverService);
# Server Running
serverRunning <- XlsToDataFrame("Data/HYSEC-ServerRunning_list.xls");
serverRunning$ServerName <- as.character(serverRunning$ServerName);
serverRunning$ServiceName <- as.character(serverRunning$ServiceName);
serverRunning$ServerStarted <- as.numeric(as.character(serverRunning$ServerStarted));
serverRunning$DaysRunning <- as.numeric(as.character(serverRunning$DaysRunning));
head(serverRunning); rm(serverRunning);
# Server Linked
serverLinked <- XlsToDataFrame("Data/HYSEC-ServerLinked_list.xls");
serverLinked$ServerName <- as.character(serverLinked$ServerName);
serverLinked$LinkedServerID <- as.integer(as.character(serverLinked$LinkedServerID));
serverLinked$LinkedServer <- as.character(serverLinked$LinkedServer);
serverLinked$Product <- as.character(serverLinked$Product);
serverLinked$Provider <- as.character(serverLinked$Provider);
serverLinked$DataSource <- as.character(serverLinked$DataSource);
serverLinked$ModificationDate <- as.numeric(as.character(serverLinked$ModificationDate));
serverLinked$IsLinked <- as.logical(as.character(serverLinked$IsLinked));
head(serverLinked); rm(serverLinked);
# Server DB spec
serverDbSpec <- XlsToDataFrame("Data/HYSEC-ServerDBSpec_list.xls");
serverDbSpec$ServerName <- as.character(serverDbSpec$ServerName);
serverDbSpec$ServiceName <- as.character(serverDbSpec$ServiceName);
serverDbSpec$DBIdentifier <- as.character(serverDbSpec$DBIdentifier);
serverDbSpec$DBName <- as.character(serverDbSpec$DBName);
serverDbSpec$OriginalDBName <- as.character(serverDbSpec$OriginalDBName);
head(serverDbSpec); rm(serverDbSpec);
# Server DB Backup
serverDbBackup <- XlsToDataFrame("Data/HYSEC-ServerDBBackup_list.xls");
serverDbBackup$ServerName <- as.character.Date(serverDbBackup$ServerName);
serverDbBackup$ServiceName <- as.character(serverDbBackup$ServiceName);
serverDbBackup$DBName <- as.character(serverDbBackup$DBName);
serverDbBackup$Backup_finish_date <- as.numeric(as.character(serverDbBackup$Backup_finish_date));
serverDbBackup$Physical_Device_name <- as.character(serverDbBackup$Physical_Device_name);
head(serverDbBackup); rm(serverDbBackup);
```

# Screening Server

## Server Usage
```{r ServerUsage, echo=TRUE, message=FALSE, warning=FALSE}
print("Server DB Usage");
## Server DB Usage
# Server DB usage list
xlsFile <- "Data/HYSEC-Usage_list.xls";
serverDbUsageList <- XlsToDataFrame(xlsFile);
serverDbUsageList$DBIdentifier <- as.numeric(as.character(serverDbUsageList$DBIdentifier));
serverDbUsageList$DBName <- as.character(serverDbUsageList$DBName);
serverDbUsageList$DBBufferPages <- as.numeric(as.character(serverDbUsageList$DBBufferPages));
serverDbUsageList$DBBufferMB <- as.numeric(as.character(serverDbUsageList$DBBufferMB));
head(serverDbUsageList);
# Server DB usage plots
usagePlot <- DBUsageDataFrameToBarplot(serverDbUsageList);
usagePieChart <- DBUsageDataFrameToPiechart(serverDbUsageList);
# Server DB usage plots all
grid.arrange(usagePlot, usagePieChart, nrow = 1, ncol = 2);
# rm
rm(serverDbUsageList); rm(usagePlot); rm(usagePieChart);
## DB All parameter
# DB All parameter list
xlsFile <- "Data/HYSEC-ParametersInFuncsAndProcs.xls";
allParametersDataFrame <- XlsToDataFrame(xlsFile);
allParametersDataFrame$ObjectName <- as.character(allParametersDataFrame$ObjectName);
allParametersDataFrame$SchemaName <- as.character(allParametersDataFrame$SchemaName);
allParametersDataFrame$ObjectTypeDesc <- as.character(allParametersDataFrame$ObjectTypeDesc);
allParametersDataFrame$ParameterID <- as.integer(as.character(allParametersDataFrame$ParameterID));
allParametersDataFrame$ParameterName <- as.character(allParametersDataFrame$ParameterName);
allParametersDataFrame$ParameterType <- as.character(allParametersDataFrame$ParameterType);
allParametersDataFrame$ParameterMaxLength <- as.integer(as.character(allParametersDataFrame$ParameterMaxLength));
allParametersDataFrame$ParameterPrecision <- as.integer(as.character(allParametersDataFrame$ParameterPrecision));
allParametersDataFrame$ParamMaxBytes <- as.integer(as.character(allParametersDataFrame$ParamMaxBytes));
allParametersDataFrame$ParameterScale <- as.integer(as.character(allParametersDataFrame$ParameterScale));
allParametersDataFrame$IsParameterOutput <- as.logical(as.character(allParametersDataFrame$IsParameterOutput));
head(allParametersDataFrame); rm(allParametersDataFrame);
```

# Screening Model
```{r Model-ObjectAll, echo=TRUE, message=TRUE, warning=FALSE}
print("Server DB Object");
## DB Object
# DB object list
xlsFile <- "Data/HYSEC-Object_list.xls";
ObjectListDataFrame <- XlsToDataFrame(xlsFile);
ObjectListDataFrame$ObjectName <- as.character(ObjectListDataFrame$ObjectName);
ObjectListDataFrame$ObjectCount <- as.integer(as.character(ObjectListDataFrame$ObjectCount));
# DB object list group fonctions
ObjectSumDataFrame <- ObjectListGroupFunctionsDataFrame(ObjectListDataFrame, "Function");
# DB object list Barplot
objectSumBarplot <- DBObjectDataFrameToBarplot(ObjectSumDataFrame);
# DB object list Piechart
objectSumPiechart <- GenericPiechartFromTwoColumnDataFrame(ObjectSumDataFrame, mainTitle = "Object Summary");
#
grid.arrange(objectSumBarplot, objectSumPiechart, nrow = 1, ncol = 2);
# DB object list all fonctions
objectAllDataFrame <- SummarizeAllDBFunctionDataFrame(ObjectListDataFrame, "Function");
objectAllBarplot <- DBFunctionDataFrameToBarplot(objectAllDataFrame);
objectAllPiechart <- DBFunctionDataFrameToPiechart(objectAllDataFrame);
# DB object list all plot
grid.arrange(objectAllBarplot, objectAllPiechart, nrow = 1, ncol = 2);
#
rm(xlsFile); rm(ObjectListDataFrame);
rm(ObjectSumDataFrame); rm(objectSumBarplot); rm(objectSumPiechart);
rm(objectAllDataFrame); rm(objectAllBarplot); rm(objectAllPiechart);
```

## Function Analysis

### Function Type List
```{r Model-Function, echo=TRUE, message=TRUE, warning=FALSE}
print("Server Function Analysis");
## Function Analysis
# Function Analysis count
xlsFile <- "Data/HYSEC-Function_count.xls";
countFunc <- XlsToDataFrame(xlsFile);
countFunc <- as.integer(as.character(countFunc$Count));
# Function Analysis list
xlsFile <- "Data/HYSEC-Function_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$FunctionName <- as.character(sqlDataFrame$FunctionName);
sqlDataFrame$FunctionID <- as.integer(as.character(sqlDataFrame$FunctionID));
sqlDataFrame$FunctionType <- as.character(sqlDataFrame$FunctionType);
sqlDataFrame$FunctionDesc <- as.character(sqlDataFrame$FunctionDesc);
sqlDataFrame$FunctionCreated <- as.numeric(as.character(sqlDataFrame$FunctionCreated)); #
sqlDataFrame$FunctionModified <- as.numeric(as.character(sqlDataFrame$FunctionModified)); #
print(paste0("Function list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# Function Analysis list barplot
fnTypeBarplot <- DataFrameColumnToBarplot(sqlDataFrame, columnName = "FunctionType");
# Function Analysis list piechart
fnTypePiechart <- DataFrameColumnToPiechart(sqlDataFrame, columnName = "FunctionType");
#
grid.arrange(fnTypeBarplot, fnTypePiechart, nrow = 1, ncol = 2);
# rm
rm(xlsFile); rm(sqlDataFrame); rm(fnTypeBarplot); rm(fnTypePiechart);
# Function Analysis param list
xlsFile <- "Data/HYSEC-Function_listParams.xls";
functionParamsDataFrame <- XlsToDataFrame(xlsFile);
functionParamsDataFrame$FunctionName <- as.character(functionParamsDataFrame$FunctionName);
functionParamsDataFrame$SchemaName <- as.character(functionParamsDataFrame$SchemaName);
functionParamsDataFrame$FunctionType <- as.character(functionParamsDataFrame$FunctionType);
functionParamsDataFrame$FunctionDesc <- as.character(functionParamsDataFrame$FunctionDesc);
functionParamsDataFrame$ParameterID <- as.integer(as.character(functionParamsDataFrame$ParameterID));
functionParamsDataFrame$ParameterName <- as.character(functionParamsDataFrame$ParameterName);
functionParamsDataFrame$ParameterType <- as.character(functionParamsDataFrame$ParameterType);
functionParamsDataFrame$ParamMaxLength <- as.integer(as.character(functionParamsDataFrame$ParamMaxLength));
functionParamsDataFrame$ParameterPrecision <- as.integer(as.character(functionParamsDataFrame$ParameterPrecision));
functionParamsDataFrame$ParameterScale <- as.integer(as.character(functionParamsDataFrame$ParameterScale));
functionParamsDataFrame$IsParamOutput <- as.logical(as.character(functionParamsDataFrame$IsParamOutput));
print(head(functionParamsDataFrame));
fnParamsDataFrameSlim <- DataFrameFromColumns(functionParamsDataFrame,
                                              "FunctionName",
                                              "FunctionType",
                                              "FunctionDesc");
print(head(fnParamsDataFrameSlim));
# Function Analysis repeat count
fnParamsDataFrameFat <- aggregate(list(NbParameters = rep(1, nrow(fnParamsDataFrameSlim))),
                                  fnParamsDataFrameSlim,
                                  length);
fnParamsDataFrameFat <- tibble::as_data_frame(fnParamsDataFrameFat);
write(summary(rev(fnParamsDataFrameFat)[1]), stdout());
# Function Analysis without params
countFuncWith <- nrow(fnParamsDataFrameFat);
# Function Analysis without params
countFuncWithout <- countFunc - countFuncWith;
# Function Analysis barplot
OutputType <- "Fn";
# Function Analysis data frame params
fnParamsDF <- DataFrameWithoutWithTotal(countFuncWithout,
                                        countFuncWith,
                                        countFunc,
                                        OutputType);
# Function Analysis param list export
print(head(fnParamsDF));
# Function Analysis barplot
fnParamsBarplot <- FunctionWithoutWithTotalDFToBarplot(fnParamsDF, OutputType);
# Function Analysis piechart
fnParamsPiechart <- FunctionWithoutWithTotalDFToPiechart(fnParamsDF, OutputType = "Function");
#
grid.arrange(fnParamsBarplot, fnParamsPiechart, nrow = 1, ncol = 2);
# Function Analysis boxplot
fnParamsBoxplot <- DBFunctionDataFrameToBoxplot(fnParamsDataFrameFat);
# Function Analysis density plot
fnParamsDensityplot <- DBFunctionDataFrameToDensityplot(fnParamsDataFrameFat);
#
grid.arrange(fnParamsBoxplot, fnParamsDensityplot, nrow = 1, ncol = 2);
# rm()
rm(xlsFile); rm(countFunc);
rm(functionParamsDataFrame); rm(fnParamsDataFrameSlim); rm(fnParamsDataFrameFat);
rm(countFuncWith); rm(countFuncWithout); rm(OutputType);
rm(fnParamsDF); rm(fnParamsBarplot); rm(fnParamsPiechart);
rm(fnParamsBoxplot); rm(fnParamsDensityplot);
```

## Procedure Analysis
```{r Model-Procedure, echo=TRUE, message=TRUE, warning=FALSE}
print("Server DB StoredProc");
## DB StoredProc
# DB StoreProc count
xlsFile <- "Data/HYSEC-Procedure_count.xls";
countStoreProc <- XlsToDataFrameSingleRow(xlsFile)$Count;
countStoreProc <- as.integer(as.character(countStoreProc));
# DB StoreProc list
xlsFile <- "Data/HYSEC-Procedure_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$ProcedureName <- as.character(sqlDataFrame$ProcedureName);
sqlDataFrame$ProcedureID <- as.integer(as.character(sqlDataFrame$ProcedureID));
sqlDataFrame$ProcedureType <- as.character(sqlDataFrame$ProcedureType);
sqlDataFrame$ProcedureDesc <- as.character(sqlDataFrame$ProcedureDesc);
sqlDataFrame$ProcedureCreated <- as.character(sqlDataFrame$ProcedureCreated);
sqlDataFrame$ProcedureModified <- as.character(sqlDataFrame$ProcedureModified);
sqlDataFrame$IsProcedureMSShipped <- as.logical(as.character(sqlDataFrame$IsProcedureMSShipped));
head(sqlDataFrame); rm(sqlDataFrame);
# DB StoreProc param list
xlsFile <- "Data/HYSEC-Procedure_listParams.xls";
storedProcParamDataFrame <- XlsToDataFrame(xlsFile);
storedProcParamDataFrame$ProcedureName <- as.character(storedProcParamDataFrame$ProcedureName);
storedProcParamDataFrame$SchemaName <- as.character(storedProcParamDataFrame$SchemaName);
storedProcParamDataFrame$ParameterType <- as.character(storedProcParamDataFrame$ProcedureType);
storedProcParamDataFrame$ProcedureDesc <- as.character(storedProcParamDataFrame$ProcedureDesc);
storedProcParamDataFrame$ParameterID <- as.integer(as.character(storedProcParamDataFrame$ParameterID));
storedProcParamDataFrame$ParameterName <- as.character(storedProcParamDataFrame$ParameterName);
storedProcParamDataFrame$ParameterType <- as.character(storedProcParamDataFrame$ParameterType);
storedProcParamDataFrame$ParamMaxLength <- as.integer(as.character(storedProcParamDataFrame$ParamMaxLength));
storedProcParamDataFrame$ParameterPrecision <- as.integer(as.character(storedProcParamDataFrame$ParameterPrecision));
storedProcParamDataFrame$ParameterScale <- as.integer(as.character(storedProcParamDataFrame$ParameterScale));
storedProcParamDataFrame$IsParamOutput <- as.logical(as.character(storedProcParamDataFrame$IsParamOutput));
storedProcParamDataFrameSlim <- DataFrameFromColumns(storedProcParamDataFrame,
                                                     "ProcedureName",
                                                     "ProcedureType",
                                                     "ProcedureDesc");
# DB StoreProc repeat count
storedProcParamDataFrameFat <- aggregate(list(NbParameters = rep(1, nrow(storedProcParamDataFrameSlim))),
                                         storedProcParamDataFrameSlim,
                                         length);
storedProcParamDataFrameFat <- tibble::as_data_frame(storedProcParamDataFrameFat);
write(summary(rev(storedProcParamDataFrameFat)[1]), stdout());
# DB StoreProc with params
countStoreProcWith <- nrow(storedProcParamDataFrameFat);
# DB StoreProc without params
countStoreProcWithout <- countStoreProc - countStoreProcWith;
# DB StoreProc data frame params
storeProcParamsDF <- DataFrameWithoutWithTotal(countStoreProcWithout,
                                               countStoreProcWith,
                                               countStoreProc,
                                               "StoreProc");
# DB StoreProc param list export
storeProcParamsDF;
# DB StoreProc barplot
OutputType <- "StoredProc";
# DB StoreProc barplot
storeProcParamsBarplot <- StoredProcWithoutWithTotalDFToBarplot(storeProcParamsDF, OutputType);
# DB StoreProc piechart
storeProcParamsPiechart <- StoredProcWithoutWithTotalDFToPiechart(storeProcParamsDF, OutputType);
#
grid.arrange(storeProcParamsBarplot, storeProcParamsPiechart, nrow = 1, ncol = 2);
# DB StoreProc boxplot
storeProcParamsBoxplot <- DBStoreProcDataFrameToBoxplot(storedProcParamDataFrameFat);
# DB StoreProc density plot
storeProcParamsDensityplot <- DBStoreProcDataFrameToDensityplot(storedProcParamDataFrameFat);
#
grid.arrange(storeProcParamsBoxplot, storeProcParamsDensityplot, nrow = 1, ncol = 2);
# rm
rm(storedProcParamDataFrame); rm(storedProcParamDataFrameFat); rm(countStoreProc); rm(countStoreProcWith);
rm(countStoreProcWithout); rm(storeProcParamsDF); rm(OutputType); rm(storeProcParamsBarplot);
rm(storeProcParamsPiechart); rm(storeProcParamsBoxplot); rm(storeProcParamsDensityplot);
```

## DB Analysis
```{r Model-DB, echo=TRUE, message=TRUE, warning=FALSE}
print("Server DB Table Count");
# DB Table Count CSV
xlsFile <- "Data/HYSEC-RowCount_list.xls";
tableRowCountDataFrame <- XlsToDataFrame(xlsFile);
tableRowCountDataFrame$TableName <- as.character(tableRowCountDataFrame$TableName);
tableRowCountDataFrame$TableRows <- as.integer(as.character(tableRowCountDataFrame$TableRows));
print(head(tableRowCountDataFrame));
# DB Table Count repeats
tableRowCountDataFrame <- aggregate(list(RowRepeats = rep(1, nrow(tableRowCountDataFrame[-1]))),
                                    tableRowCountDataFrame[-1],
                                    length);
tableRowCountDataFrame <- tibble::as_data_frame(tableRowCountDataFrame);
print(head(tableRowCountDataFrame));
# DB Table Count half > mean repeats
aMean <- mean(tableRowCountDataFrame$RowRepeats);
tableRowCountDataFrame <- subset(tableRowCountDataFrame, RowRepeats > aMean);
print(head(tableRowCountDataFrame));
# DB Table Count barplot
tableRowCountBarplot <- DBRowCountFrameToBarplot(tableRowCountDataFrame);
tableRowCountBarplot;
# rm()
rm(xlsFile); rm(tableRowCountDataFrame); rm(aMean);  rm(tableRowCountBarplot);
```

## Table Analysis
```{r Model-TableAnalysis, echo=TRUE, message=TRUE, warning=FALSE}
print("Server DB Table Analysis");
## DB Table Analysis
# DB Table Analysis count
xlsFile <- "Data/HYSEC-Table_count.xls";
countTable <- XlsToDataFrame(xlsFile);
print(paste0("Table Analysis count: ", countTable$Count));
# rm()
rm(xlsFile); rm(countTable);
# DB Table Analysis list
xlsFile <- "Data/HYSEC-Table_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableName <- as.character(sqlDataFrame$TableName);
sqlDataFrame$TableID <- as.integer(as.character(sqlDataFrame$TableID));
sqlDataFrame$TableType <- as.character(sqlDataFrame$TableType);
sqlDataFrame$TableDesc <- as.character(sqlDataFrame$TableDesc);
sqlDataFrame$TableCreated <- as.numeric(as.character(sqlDataFrame$TableCreated)); #
sqlDataFrame$TableModified <- as.numeric(as.character(sqlDataFrame$TableModified)); #
sqlDataFrame$MaxColumnIDUsed <- as.integer(as.character(sqlDataFrame$MaxColumnIDUsed));
sqlDataFrame$IsUsingANSINulls <- as.logical(as.character(sqlDataFrame$IsUsingANSINulls));
sqlDataFrame$LOBDataSpaceID <- as.integer(as.character(sqlDataFrame$LOBDataSpaceID));
print(head(sqlDataFrame));
# rm()
rm(xlsFile); rm(sqlDataFrame);
```

### Table Independent List
Verify if empty or not used.
```{r Model-TableIndependentList, echo=TRUE, message=TRUE, warning=FALSE}
print("Server DB Table Independent List");
# DB Table Analysis Independent
xlsFile <- "Data/HYSEC-TableIndependent_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableWoParentWoDependents <- as.character(sqlDataFrame$TableWoParentWoDependents);
sqlDataFrame$TableID <- as.integer(as.character(sqlDataFrame$TableID));
sqlDataFrame$TableType <- as.character(sqlDataFrame$TableType);
sqlDataFrame$TableDesc <- as.character(sqlDataFrame$TableDesc);
sqlDataFrame$TableCreated <- as.numeric(as.character(sqlDataFrame$TableCreated)); #
sqlDataFrame$TableModified <- as.numeric(as.character(sqlDataFrame$TableModified)); #
sqlDataFrame$MaxColumnIDUsed <- as.integer(as.character(sqlDataFrame$MaxColumnIDUsed));
sqlDataFrame$IsUsingANSINulls <- as.logical(as.character(sqlDataFrame$IsUsingANSINulls));
sqlDataFrame$LOBDataSpaceID <- as.integer(as.character(sqlDataFrame$LOBDataSpaceID));
print(paste0("Table Independent list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# rm()
rm(xlsFile); rm(sqlDataFrame);
```

### Table Trunk List
Verify if empty or not used.
Verify if FK point to indexed columns.
Verify if PK is indexed.
```{r Model-TableTrunkList, echo=TRUE, message=TRUE, warning=FALSE}
print("Server DB Table Trunk List");
# DB Table Analysis Trunk
xlsFile <- "Data/HYSEC-TableTrunk_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableLeafName <- as.character(sqlDataFrame$TableTrunkName);
print(paste0("Table Trunk list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# rm()
rm(xlsFile); rm(sqlDataFrame);
```

### Table Leaf List
Verify if empty or not used.
Verify if FK point to indexed columns.
Verify if PK is indexed.
```{r Model-TableLeafList, echo=TRUE, message=TRUE, warning=FALSE}
print("Table Leaf List");
# DB Table Analysis Leaf
xlsFile <- "Data/HYSEC-TableLeaf_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableWoParentWoDependents <- as.character(sqlDataFrame$TableLeafName);
print(paste0("Table Leaf list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# rm()
rm(xlsFile); rm(sqlDataFrame);
```

### Table Parent List
Verify if empty or not used.
Verify if PK is indexed.
```{r Model-TableParentList, echo=TRUE, message=TRUE, warning=FALSE}
print("Table Parent List");
# DB Table Analysis Parent
xlsFile <- "Data/HYSEC-TableParent_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableParent <- as.character(sqlDataFrame$TableParent);
sqlDataFrame$TableChild <- as.character(sqlDataFrame$TableChild);
sqlDataFrame$FKName <- as.character(sqlDataFrame$FKName);
print(paste0("Table Parent list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# rm()
rm(xlsFile); rm(sqlDataFrame);
```

### Table Key List
Verify if FK point to indexed columns.
Verify if PK is indexed.
```{r Model-TableKeyList, echo=TRUE, message=TRUE, warning=FALSE}
print("Table Key List");
# DB Table Analysis keys list
xlsFile <- "Data/HYSEC-Table_listKeys.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableName <- as.character(sqlDataFrame$TableName);
sqlDataFrame$PKName <- as.character(sqlDataFrame$PKName);
sqlDataFrame$FKName <- as.character(sqlDataFrame$FKName);
sqlDataFrame$ColumnName <- as.character(sqlDataFrame$ColumnName);
print(paste0("Table Key list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# rm()
rm(xlsFile); rm(sqlDataFrame);
```

## View Analysis
Check if they are indexable or indexed, index them if needed to increase performance.
```{r Model-View, echo=TRUE, message=TRUE, warning=FALSE}
print("Server View Analysis");
## View Analysis
# View Analysis count
xlsFile <- "Data/HYSEC-View_count.xls";
countView <- XlsToDataFrame(xlsFile);
countView <- as.integer(as.character(countView$Count));
# View Analysis list
xlsFile <- "Data/HYSEC-View_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$ViewName <- as.character(sqlDataFrame$ViewName);
sqlDataFrame$ViewID <- as.integer(as.character(sqlDataFrame$ViewID));
sqlDataFrame$ViewType <- as.character(sqlDataFrame$ViewType);
sqlDataFrame$ViewDesc <- as.character(sqlDataFrame$ViewDesc);
sqlDataFrame$ViewCreated <- as.numeric(as.character(sqlDataFrame$ViewCreated)); #
sqlDataFrame$ViewModified <- as.numeric(as.character(sqlDataFrame$ViewModified)); #
sqlDataFrame$IsIndexed <- as.integer(as.character(sqlDataFrame$IsIndexed));
sqlDataFrame$IsIndexable <- as.integer(as.character(sqlDataFrame$IsIndexable));
print(paste0("View list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# rm()
rm(countView); rm(xlsFile); rm(sqlDataFrame);
```

## Principal Key Analysis
Check if all are used nor indexed.
```{r Model-PrincipalKey, echo=TRUE, message=TRUE, warning=FALSE}
print("Server PKey Analysis");
## PKey Analysis
# PKey Analysis count
xlsFile <- "Data/HYSEC-PKeys_count.xls";
countPKeys <- XlsToDataFrame(xlsFile);
countPKeys <- as.character(countPKeys$Count);
# PKey Analysis list
xlsFile <- "Data/HYSEC-PKeys_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableName <- as.character(sqlDataFrame$TableName);
sqlDataFrame$ColumnName <- as.character(sqlDataFrame$ColumnName);
sqlDataFrame$PrincipalKey <- as.character(sqlDataFrame$PrincipalKey);
sqlDataFrame$PrincipalKeyID <- as.integer(as.character(sqlDataFrame$PrincipalKeyID));
sqlDataFrame$PKCreated <- as.numeric(as.character(sqlDataFrame$PKCreated));
sqlDataFrame$PKModified <- as.numeric(as.character(sqlDataFrame$PKModified));
sqlDataFrame$PKOrdinal <- as.integer(as.character(sqlDataFrame$PKOrdinal));
print(paste0("PKey list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# PKey Analysis list histogram
aTable <- ColumnDataFrameToFrequencyTable(sqlDataFrame, columnName = "TableName");
aTibble <- FrequencyTableToTibble(aTable, aTitle = "PrincipalKeyTable");
principalKeyHistogram <- TwoColumnDataFrameToHistogram(aTibble, mainTitle = "PrincipalKey per Table");
# rm
rm(countPKeys); rm(xlsFile); rm(sqlDataFrame);
rm(aTable); rm(aTibble); rm(principalKeyHistogram);
```

## Foreign Key Analysis
Check if all are used nor indexed nor trusted.
Verify tables if ON Delete CASCADE.
```{r Model-ForeignKey, echo=TRUE, message=TRUE, warning=FALSE}
print("Server FKey Analysis");
## FKey Analysis
# FKey Analysis count
xlsFile <- "Data/HYSEC-FKeys_count.xls";
countFKeys <- XlsToDataFrame(xlsFile);
countFKeys <- as.integer(as.character(countFKeys$Count));
# FKey Analysis list
xlsFile <- "Data/HYSEC-FKeys_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableName <- as.character(sqlDataFrame$TableName);
sqlDataFrame$ColumnName <- as.character(sqlDataFrame$ColumnName);
sqlDataFrame$ForeignKey <- as.character(sqlDataFrame$ForeignKey);
sqlDataFrame$ForeignKeyID <- as.character(sqlDataFrame$ForeignKey);
sqlDataFrame$ReferenceTableName <- as.character(sqlDataFrame$ReferenceTableName);
sqlDataFrame$ReferenceColumnName <- as.character(sqlDataFrame$ReferenceColumnName);
sqlDataFrame$FKCreated <- as.numeric(as.character(sqlDataFrame$FKCreated));
sqlDataFrame$FKModified <- as.numeric(as.character(sqlDataFrame$FKModified));
sqlDataFrame$FKnotTrusted <- as.logical(as.character(sqlDataFrame$FKnotTrusted));
sqlDataFrame$OnDelete <- as.character(sqlDataFrame$OnDelete);
sqlDataFrame$OnUpdate <- as.character(sqlDataFrame$OnUpdate);
print(paste0("FKeys list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# FKey Analysis list histogram
aTable <- ColumnDataFrameToFrequencyTable(sqlDataFrame, columnName = "TableName");
aTibble <- FrequencyTableToTibble(aTable, aTitle = "PrincipalKeyTable");
fKeyHistogram <- TwoColumnDataFrameToHistogram(aTibble, mainTitle = "ForeignKey per Table");
# rm
rm(countFKeys); rm(xlsFile); rm(sqlDataFrame);
rm(aTable); rm(aTibble); rm(fKeyHistogram);
```

## Index Analysis

### Index List
```{r Model-Indexes, echo=TRUE, message=TRUE, warning=FALSE}
print("Server Index Analysis");
## Index Analysis
# Index Analysis count
xlsFile <- "Data/HYSEC-Index_count.xls";
countIndex <- XlsToDataFrame(xlsFile);
countIndex <- as.integer(as.character(countIndex$Count));
# Index Analysis list
xlsFile <- "Data/HYSEC-Index_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$DBName <- as.character(sqlDataFrame$DBName);
sqlDataFrame$TableName <- as.character(sqlDataFrame$TableName);
sqlDataFrame$ColumnNumber <- as.integer(as.character(sqlDataFrame$ColumnNumber));
sqlDataFrame$ColumnName <- as.character(sqlDataFrame$ColumnName);
sqlDataFrame$ConstraintName <- as.character(sqlDataFrame$ConstraintName);
sqlDataFrame$ConstraintType <- as.character(sqlDataFrame$ConstraintType);
sqlDataFrame$ConstraintDescription <- as.character(sqlDataFrame$ConstraintDescription);
sqlDataFrame$CreatedDate <- as.numeric(as.character(sqlDataFrame$CreatedDate));#
sqlDataFrame$ConstraintDefinition <- as.character(sqlDataFrame$ConstraintDefinition);
sqlDataFrame$UsesDBCollation <- as.logical(as.character(sqlDataFrame$UsesDBCollation));
sqlDataFrame$IsSystemNamed <- as.logical(as.character(sqlDataFrame$IsSystemNamed));
print(head(sqlDataFrame));
# Index Analysis list histogram
aTable <- ColumnDataFrameToFrequencyTable(sqlDataFrame, columnName = "TableName");
aTibble <- FrequencyTableToTibble(aTable, aTitle = "IndexPerTable");
indexesHistogram <- TwoColumnDataFrameToHistogram(aTibble, mainTitle = "Index per Table");
# rm
rm(countIndex); rm(xlsFile); rm(sqlDataFrame);
rm(aTable); rm(aTibble); rm(indexesHistogram);
# Index Analysis type list
xlsFile <- "Data/HYSEC-Index_listTypes.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$TableName <- as.character(sqlDataFrame$TableName);
sqlDataFrame$TableType <- as.character(sqlDataFrame$TableType);
sqlDataFrame$TableDesc <- as.character(sqlDataFrame$TableDesc);
sqlDataFrame$TableIndexID <- as.integer(as.character(sqlDataFrame$TableIndexID));
sqlDataFrame$IndexName <- as.character(sqlDataFrame$IndexName);
sqlDataFrame$IndexID <- as.integer(as.character(sqlDataFrame$IndexID)) ;
sqlDataFrame$IndexType <- as.character(sqlDataFrame$IndexType);
sqlDataFrame$ConstraintType <- as.character(sqlDataFrame$ConstraintType);
sqlDataFrame$AllocUnitID <- as.numeric(as.character(sqlDataFrame$AllocUnitID));
print(paste0("Index Type list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
# rm
rm(xlsFile); rm(sqlDataFrame);
```
Verify Constraint Type.
Verify if can lock page.

## Constraint Analysis
Validate if constraint is respected.
```{r Model-Constraint, echo=TRUE, message=TRUE, warning=FALSE}
print("Server Constraint Analysis");
## Constraint Analysis
# Constraint Analysis List
xlsFile <- "Data/HYSEC-Constraint_list.xls";
sqlDataFrame <- XlsToDataFrame(xlsFile);
sqlDataFrame$DBName <- as.character(sqlDataFrame$DBName);
sqlDataFrame$TableName <- as.character(sqlDataFrame$TableName);
sqlDataFrame$ColumnNumber <- as.integer(as.character(sqlDataFrame$ColumnNumber));
sqlDataFrame$ColumnName <- as.character(sqlDataFrame$ColumnName);
sqlDataFrame$ConstraintName <- as.character(sqlDataFrame$ConstraintName);
sqlDataFrame$ConstraintType <- as.character(sqlDataFrame$ConstraintType);
sqlDataFrame$ConstraintDescription <- as.character(sqlDataFrame$ConstraintDescription);
#
sqlDataFrame$ConstraintDefinition <- as.character(sqlDataFrame$ConstraintDefinition);
print(paste0("Constraint list count: ", nrow(sqlDataFrame)));
print(head(sqlDataFrame));
sqlDataFrame <- ConstraintToTableNameFrequency(sqlDataFrame);
constraintBarplot <- TwoColumnDataFrameToBarlot(sqlDataFrame);
constraintBarplot;
# rm()
rm(xlsFile); rm(sqlDataFrame); rm(constraintBarplot);
```
